Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-28 fmics/paper.tex
improve/fill in proof paragraph

To prove Theorem~(\ref{output_input_at_update_times}), we first make the following observations, for sufficiently large $t$:
\begin{enumerate}
\item
$\mathsf{SR}\;D\;n\;(m+1)\;t=\mathsf{SR}\;D\;n\;m\;(t-\mathsf{delay}\;n)$, since shift register cells get their values from the previous cell, but only update every $\mathsf{delay}\;n$ time steps;
\item
$\mathsf{SR}\;D\;n\;m\;t=\mathsf{SR}\;D\;n\;0\;(t-(m\times\mathsf{delay}\;n))$, by induction on $m$ using the result above;
\item
$\mathsf{output}\;D\;n\;x\;t$ is the sum of values of consecutive shift register cells (Theorem~(\ref{output_sum})), by induction on $t$;
\item
Combining the last two results, $\mathsf{output\;D\;n\;x\;t}$ is the sum of consecutive values of the first shift register cell, $\mathsf{SR\;D\;n\;0}$;
\item
<Thus Theorem~(\ref{output_prev_at_update_times}), because the first shift register cell gets its value from the output of a previous slice>
\item
<Now that we have expressed one output in terms of a previous output, Theorem~(\ref{output_input_at_update_times}) can be proved by induction on $n$ (but this is not trivial - need to check what else apart from $\ref{output_prev_at_update_times}$ is really needed for the inductive step)>
\end{enumerate}

>>>>

To prove Theorem~(\ref{output_input_at_update_times}), we first make the following observations\footnote{The precise statements of these observations are complicated by details of what happens when $t$ is low, or equivalently, when we are looking at shift register cells that have not yet received any input.}
\begin{enumerate}
\item
$\mathsf{SR}\;D\;n\;(m+1)\;t=\mathsf{SR}\;D\;n\;m\;(t-\mathsf{delay}\;n)$, since shift register cells get their values from the previous cell, but only update every $\mathsf{delay}\;n$ time steps;
\item
$\mathsf{SR}\;D\;n\;m\;t=\mathsf{SR}\;D\;n\;0\;(t-(m\times\mathsf{delay}\;n))$, by induction on $m$ using the result above;
\item
$\mathsf{output}\;D\;n\;x\;t$ is a sum of values of consecutive shift register cells (Theorem~(\ref{output_sum})), which can be proved by induction on $t$;
\item
Combining the last two results, $\mathsf{output}\;D\;n\;x\;t$ is a sum of consecutive values of the first shift register cell, $\mathsf{SR}\;D\;n\;0$;
\item
Thus, we can express $\mathsf{output}\;D\;n\;x\;t$ in terms of $\mathsf{output}\;D\;n'\;x'\;t$, where $(n',x')=\mathsf{input}\;n$, since the source of $\mathsf{SR}\;D\;n\;0$ is the previous (input) slice's output;
\item
Finally, by induction on $n$, we can express $\mathsf{output}\;D\;n\;x\;t$ as a function of $D$ alone, as in Theorem~(\ref{output_input_at_update_times}), using the result above for the inductive case.
\end{enumerate}
